Full Dissertation

### 2024-04-09 Sections/HTW.qmd
fix igas crossrefs; add callout styling
add e3 summary and tweak some table captions

[Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}

_______________________________________________________________________________

@@

: **Experiment 3 testing accuracy**. Main effects of condition and band type (training vs. extrapolation), and the interaction between the two factors. Larger coefficient estimates indicate larger deviations from the baselines (constant training;  trained bands & original order) - and a positive interaction coefficient indicates disproportionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
:::

@@

Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band {.striped .hover .sm}
:::

@@

>>>>

[Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
_______________________________________________________________________________

@@

: **Experiment 3 testing accuracy**. Main effects of condition and band type (training vs. extrapolation), and the interaction between the two factors. The Intercept represents the baseline condition, (constant training;  trained bands & original order), and the remaining coefficients reflect the deviation from that baseline. Positive coefficients thus represent worse performance relative to the baseline,  - and a positive interaction coefficient indicates disproportionate deviation for the varied condition or reverse order condition.{.striped .hover .sm}
:::

@@

Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band. The Intercept represents the baseline condition (constant training & original order), and the Band coefficient represents the linear slope for the baseline condition.  {.striped .hover .sm}
:::

@@

In Experiment 3, we investigated the effects of training condition (constant vs. varied) and band type (training vs. extrapolation) on participants' accuracy and discrimination during the testing phase. Unlike the previous experiments, participants received ordinal feedback during the training phase. Additionally, Experiment 3 included both the original order condition from Experiment 1 and the reverse order condition from Experiment 2. The results revealed no significant main effects of training condition on testing accuracy, nor was there a significant difference between groups in band discrimination.  However, we observed a significant three-way interaction for the discrimination analysis, indicating that the varied condition showed a steeper slope coefficient on the reverse order bands compared to the constant condition. This result suggests that varied training enhanced participants' ability to discriminate between velocity bands, but only when the band order was reversed during testing.

### 2024-04-09 Sections/full.qmd
add e3 summary and tweak some table captions

The study of human function learning investigates how people learn relationships between continuous input and output values.  Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021a; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].

@@

: **Experiment 3 testing accuracy**. Main effects of condition and band type (training vs. extrapolation), and the interaction between the two factors. Larger coefficient estimates indicate larger deviations from the baselines (constant training;  trained bands & original order) - and a positive interaction coefficient indicates disproportionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
:::

@@

Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band {.striped .hover .sm}
:::

>>>>

The study of human function learning investigates how people learn relationships between continuous input and output values.  Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].

@@

: **Experiment 3 testing accuracy**. Main effects of condition and band type (training vs. extrapolation), and the interaction between the two factors. The Intercept represents the baseline condition, (constant training;  trained bands & original order), and the remaining coefficients reflect the deviation from that baseline. Positive coefficients thus represent worse performance relative to the baseline,  - and a positive interaction coefficient indicates disproportionate deviation for the varied condition or reverse order condition.  {.striped .hover .sm}
:::

@@

Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band. The Intercept represents the baseline condition (constant training & original order), and the Band coefficient represents the linear slope for the baseline condition. .hover .sm}
:::
